Legacy Data Confounds Modern Genomics Studies

### 2018-09-04 legacy.tex
minor changes to remove errors

\subsection{Genome Wide Association Study}
Using an in-house R script, we performed a logistic regression using the glm package. \cite{[R and GLM]} We performed this statistical test independently for each population of the 1kGP. The deviations from the null model for each test was used to compute the chi-squared p value for each SNP for each population. Since each deviation follows a chi-squared distribution, the sum of the deviations also follow a chi-squared distribution. However, since not all SNPs are present in all populations, when computing the p values for the summed deviations, the degrees of freedom were adjusted to the number of populations tested.

@@

\bibliographystyle{plain}
\bibliography{Legacy.bib}

\subsection{Supplementary Figures}
\renewcommand{\thefigure}{S\arabic{figure}}
\setcounter{figure}{0}

@@

\caption{Manhattan plot of the -log10 p values for the combined test using the deviations from each population of the 1kGP. 
There are 3990 variants that reach p values greater than $ p < 0.01$ after performing a two-stage Benjamini & Hochberg FDR adjustment. 
The circles ( o ) are SNPs that reached values greater than 20, for clarity we implemented hard ceiling at 20.}
  \label{Manhattan}
\end{figure}

>>>>

\subsection{Genome Wide Association Study}
Using an in-house R script, we performed a logistic regression using the glm package. \cite{R,GLM} We performed this statistical test independently for each population of the 1kGP. The deviations from the null model for each test was used to compute the chi-squared p value for each SNP for each population. Since each deviation follows a chi-squared distribution, the sum of the deviations also follow a chi-squared distribution. However, since not all SNPs are present in all populations, when computing the p values for the summed deviations, the degrees of freedom were adjusted to the number of populations tested.

@@

%\bibliographystyle{plain}
\bibliography{Legacy.bib}

\section{Supplementary Figures}
\renewcommand{\thefigure}{S\arabic{figure}}
\setcounter{figure}{0}

@@

\caption{Manhattan plot of the -log10 p values for the combined test using the deviations from each population of the 1kGP. 
There are 3990 variants that reach p values greater than $ p < 0.01$ after performing a two-stage Benjamini and Hochberg FDR adjustment. 
The circles ( o ) are SNPs that reached values greater than 20, for clarity we implemented hard ceiling at 20.}
  \label{Manhattan}
\end{figure}
